Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-08-09 paper.tex
possible conclusion revisions

In this work, we developed automatically generated OpenCL codes for SIMD and SIMT-vectorized evaluations of thermochemical source-term and sparse\slash dense chemical kinetic Jacobian matrices.
The main contributions of this work are:
\begin{itemize}
 \item Deriving and verifying a new Jacobian formulation for \texttt{pyJac} that greatly increases sparsity;
 \item Extending \texttt{pyJac} to enable vectorized execution on the CPU, GPU, and other accelerators; and
 \item Achieving significant speedups over a strictly parallel Jacobian and source-term evaluation on SIMD-enabled processors (e.g., CPUs).
\end{itemize}

The new molar-based formulation for \texttt{pyJac} resulted in highly sparse chemical kinetic Jacobians,
and allows selection of either the constant-volume or constant-pressure approximation.
In addition, sparsity can be increased further by eliminating components associated with the bath gas, as discussed in \cref{S:sparsity};
this approximation is not a key feature of this work, and future efforts to develop more sophisticated Jacobian approximations based on the \texttt{pyJac} software would be a worthwhile endeavor.

>>>>

In this work, we developed automatically generated OpenCL codes for SIMD and SIMT-vectorized evaluations of thermochemical source-term and sparse\slash dense chemical kinetic Jacobian matrices.
The main contributions of this work are:
\begin{itemize}
 \item Deriving and \add{reproducibly} verifying a new Jacobian formulation \revisedelete{for \texttt{pyJac}} that greatly increases sparsity;
 \item \revisedelete{Extending \texttt{pyJac} to enable}\add{Enabling} vectorized execution on the CPU, GPU, and other accelerators; and
 \item Achieving significant speedups over a strictly parallel Jacobian and source-term evaluation on SIMD-enabled processors (e.g., CPUs).
\end{itemize}

\add{These achievements are made publicly available (see~\cref{A:availability}) via the open-source, high-performance, chemical kinetics code \texttt{pyJac}}.
The new molar-based formulation \revisedelete{for \texttt{pyJac}} resulted in highly sparse chemical kinetic Jacobians, and allows selection of either the constant-volume or constant-pressure approximation.
In addition, sparsity can be increased further by eliminating components associated with the bath gas, as discussed in \cref{S:sparsity}; this approximation is not a key feature of this work, and future efforts to develop more sophisticated Jacobian approximations based on the \texttt{pyJac} software would be a worthwhile endeavor.
